---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# simplygraph

simplygraph provides functions to simplify graph topologies.

## Installation

You can install the development version of simplygraph from [GitHub](https://github.com/dSHARP-CMU/simplygraph) with:

``` r
# install.packages("devtools")
devtools::install_github("dSHARP-CMU/simplygraph")
```

## Example

Say you have a graph where multiple nodes could be removed while still maintaining the same intersections between paths:

```{r build, message=FALSE}
set.seed(100)
library(igraph)
library(simplygraph)

graph <- graph_from_edgelist(
  matrix(c(
    "a", "b",
    "b", "f",
    "b", "c",
    "c", "d",
    "d", "e",
    "e", "f",
    "f", "g",
    "d", "h",
    "h", "i"
  ), ncol = 2, byrow = TRUE),
  directed = FALSE
)

plot(graph)
```

Nodes `e`, `c`, and `h` could be removed without fundamentally altering the relationship of path intersections in this graph. `simplify_topology()` finds those 2-degree nodes and removes them, rewiring the remaining tangent nodes.

```{r simplify, message=FALSE}
simple_graph <- simplify_topology(graph)

plot(simple_graph)
```
